\documentclass[12pt]{article}
\begin{document}
\title{ATM Database Management System}
\author{K Naveen Kumar(201451074)\\Charu Chhimpa(201451073)\\Mounika Maheshwari(201451062)}
\maketitle


\begin{itemize}

\item \textbf{Description}

\begin{itemize}



\item  Our database is about helping user while withdrawing and transferring money from ATM .
\item The proposed system maintains all the records in computerized form.

\end{itemize}


\item \textbf{ATM} 

\begin{itemize}
\item An Automated Teller Machine(ATM) is a computerized telecommunications device that provides the customers of a financial institution with access to financial transaction in a public space without the need for a human clerk or bank teller.
\end{itemize}

\item \textbf{Data Requirements}
\begin{itemize}
\item various banks(id's,name,address)
\item bankbranches(branchid,bankid,name,address)
\item customers details(name,id given by bank,other details)
\item accounts holded by customers(account id,customerid,other details)
\item customers cards(card numbers,account id)
\item atm machines(atm id,customer branch id,location)
\item atm machines services(service type code)
\item withdrawl details(id,atmid,cardno.,)
\end{itemize}

Here we are assuming that bank is maintaing its account database on its own and any updates from the atm will be automatically updated in the particular bank account.
\item \textbf{Scope}\\

Our database serves the users in following ways.
\begin{itemize}
\item Before opening an account in a particular branch ,a user can look into the availability of atm centers and open accordingly in the appropriate bank.
\item With the help of this system user can see all record about his account.
\item He can also look into the services provided by the atm machine of that bank eg.balance withdrawl,checking balance,other enquiries.
\item We can find which bank has more branches,more atm centers in that area(by looking into its location)
\item We will answer quiries like all the cards that customer has with his account and the withdrawls that he performed and manage the money availability in his account.


\end{itemize}
\end{itemize}

\end{document}

